---
title: "ixplorer gadgets"
author: "ixpantia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ixplorer gadgets

ixplorer gadgets are a way to create and check your project issues without 
leaving RStudio and more important without interrupting your workflow.

# How to use the ixplorer gadgets

First you have to install your ixplorer package

```{r, eval = FALSE}
install.packages("ixplorer")
```

When you are done with the installation, you are going to be able to see in
the *Addins* menu, under the IXPLORER title, three options:

 - Authenticate
 - Create issue
 - ixplorer issues
 

## Authenticate gadget

This is the first step in order to be able to create issues or check you project
issues with the ixplorer gadgets. You will need an API key (provided by your
project  manager).

!["img/authentication_gadget.png"]

At the **ixplorer url** make sure to include the web direction of your
ixplorer repository. It has to be similar to: _https://ixplorer_name.ixpantia.com/_

The the next step is to fullfill the name of the **upstream project**. This is the
project where the repository resides. A project can have several repositories. In
this case we just need the name of the project.

At the **ixplorer repository name** we have to write the name of the specific
repository where we are going to work

Finally we have the space for write our user name. In the section **ixplorer user name**  This is the same user name that we use to access to the ixplorer environment.

There is an option of a **persist token**. If we are working in our computer, we
can select this option. What this is going to do, is to keep all this authentication data for the next session we have. In this order we can avoid 
doing the authentication each time that we are going to work in the same
repository.

Be careful because if you`re working in somebodyelse computer, your personal
authentication data is going to be store in that computer. Avoid this action
leaving the option without a mark.

## Create issue gadget

At this point you should have all your authentication done. If that is correct
you are going to be able to create an issue without getting out of RStudio!

If everything is okay, you are just going to see the **issue title** and **Description** section. If not, you`re going to see a  





 


